\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-18 paper.tex
Contribution Rachid - Bringing human into equation

\subsubsection{Modelling the Humans}

\fxfatal{Re-organise, rephrase, complement}

@@

The cognitive model that the robot builds for the agent it interacts with is
still simple and mostly focused on geometric features (\emph{Who sees what? What are
our relative positions?} etc.). Extending this knowledge with more subtle
perceptions (emotional state for instance) remains to be done.

We should also mention that modelling of human behaviours also appear in our
architecture at the level of task and motion planning with a set of
\emph{social rules}, including proxemics, action legibility or time
optimization.

>>>>

One essential and incredibly complex question is the consideration of
humans in the system, how they are modeled and how these models are
used by the robot to perceive and interpret their motion and action,
to synthesize its behaviour in order to act on the environment and to
interact with its human partners.

We claim that it is possible and useful to devise and use models of
the humans, how they act, their needs and preferences. This can be
done in very limited, but still interesting and useful, contexts such
as collaborative human-robot objects manipulation, fetch-and-carry and
associated activities in a domestic or professional environment.

\subsubsection{Estimate human mental state}

@@

The cognitive model that the robot builds for the agent it interacts with is
still simple and mostly focused on geometric features and affordances (\emph{Who sees what? What are
our relative positions? reachability estimation}  etc.). Extending this knowledge with more subtle
perceptions (emotional state for instance) remains to be done.

\subsubsection{Motion and action execution in close vicinity to the human}

The human model we use embeds also human preferences and associated
constraints that could be taken into account when synthesizing robot motion
or elaborating robot plans.

This includes proxemics (human-robot distance) and associated issues
(visibility) but also legibility and acceptability criterias
expressed in terms of \emph{social rules} that the elaborated plans should
satisfy.
